---
title: "Juvenile salmon from GOAIERP"
author: "Alberto Rovellini"
date: "12/3/2021"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(rbgm)
library(sf)
library(maps)
library(mapdata)
library(viridis)
```

```{r}
select <- dplyr::select
```


This document produces distribution maps for juvenile salmon in the GOA based on the GOAIERP survey data analysed with sdmTMB. The sdmTMB workflow was based on distance from shore.

Some notes:

1. The surveys really only focus on the central GOA, and the sdmTMB predictions span from AI to BC. This is likely a big approximation and may be outright wrong.
2. From Jamal, regarding the designation of life stages: 'The juvenile and immature designations are for salmon. Juvenile is the first year at sea (will turn 1 Jan 1st) and immature are salmon older than 1st year of life in the ocean'. Not much adult salmon in that data, at all, only some undetermined sockeye. Here I am only using the juveniles (J) to map distributions, same as we used J only for the diets.
3. No seasonal definition here, and since these are summer surveys really that is what we are deriving - summer distributions.

So many limitations, but better than forcing them as Ruggerone and Irvine (2018). 


Read in the biomass estimates from the GOAIERP workflow.
```{r}
chinook_data <- read.csv('C:/Users/Alberto Rovellini/Documents/GOA/SDM/GOAIERP/output/biomass/SCH_J_GOAIERP.csv')
chum_data <- read.csv('C:/Users/Alberto Rovellini/Documents/GOA/SDM/GOAIERP/output/biomass/SCM_J_GOAIERP.csv')
coho_data <- read.csv('C:/Users/Alberto Rovellini/Documents/GOA/SDM/GOAIERP/output/biomass/SCO_J_GOAIERP.csv')
pink_data <- read.csv('C:/Users/Alberto Rovellini/Documents/GOA/SDM/GOAIERP/output/biomass/SPI_J_GOAIERP.csv')
sockeye_data <- read.csv('C:/Users/Alberto Rovellini/Documents/GOA/SDM/GOAIERP/output/biomass/SSO_J_GOAIERP.csv')
```

Read in spatial data.
```{r}
atlantis_bgm <- read_bgm('data/GOA_WGS84_V4_final.bgm')
atlantis_box <- atlantis_bgm %>% box_sf()
atlantis_bbox <- atlantis_box %>% st_bbox()
atlantis_crs <- atlantis_bgm$extra$projection

# some coast
# add coastline 
coast <- map("worldHires", regions = c("USA","Canada"), plot = FALSE, fill = TRUE)
coast_sf <- coast %>% st_as_sf() %>% st_transform(crs=atlantis_crs) %>% st_combine()
```

Now expand the biomass output to missing boxes.
```{r}
salmon_list <- list(chinook_data,chum_data,coho_data,pink_data,sockeye_data)
names(salmon_list) <- c('SCH','SCM','SCO','SPI','SSO')

expand_biomass <- function(salmon_data){

  salmon_all_boxes <- atlantis_box %>%
    select(box_id,botz,boundary,area) %>%
    full_join(salmon_data, by = c('box_id','boundary')) %>%
    select(box_id,botz,boundary,biomass,area.x) %>%
    mutate(biomass = replace_na(biomass,0),
           prop=biomass/sum(biomass))
  
  min_prop <- salmon_all_boxes %>% filter(prop>0, boundary==F, botz<0) %>% pull(prop) %>% min()
  max_prop <- salmon_all_boxes %>% filter(prop>0, boundary==F, botz<0) %>% pull(prop) %>% max()
  
  box_no_salmon <- salmon_all_boxes %>% filter(prop==0, boundary==F, botz<0) %>% nrow()
  
  salmon_all_boxes$prop[salmon_all_boxes$prop==0 & salmon_all_boxes$boundary==F & salmon_all_boxes$botz<0] <- min_prop
  salmon_all_boxes$prop[salmon_all_boxes$prop==max_prop] <- salmon_all_boxes$prop[salmon_all_boxes$prop==max_prop] - (box_no_salmon*min_prop)
  
  salmon_all_boxes

}

t<- lapply(salmon_list, expand_biomass)

for(i in 1:length(salmon_list)){
  # make plots
  
  p <- t[[i]] %>%
    ggplot()+
    geom_sf(aes(fill=biomass/area.x))+
    scale_fill_viridis()+
    geom_sf(data=coast_sf)+
    coord_sf(xlim=c(atlantis_bbox$xmin,atlantis_bbox$xmax),ylim=c(atlantis_bbox$ymin,atlantis_bbox$ymax))+
    theme_bw()+
    labs(title=names(salmon_list)[[i]])
  
  ggsave(paste0(names(salmon_list)[[i]],'_J.png'),p)
  
  #write out table
  t[[i]] %>% st_set_geometry(NULL) %>% select(box_id,prop) %>% write.csv(paste0(names(salmon_list)[[i]],'_J.csv'), row.names = FALSE)
}
```



